
\documentclass[letterpaper, 11 pt, conference]{ieeeconf} 
\IEEEoverridecommandlockouts
\overrideIEEEmargins

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed


%% \usepackage{amsmath}
%% \usepackage{amssymb}
%% \usepackage{gensymb} 
%% \usepackage{dsfont}
%% \usepackage{graphicx}
%% \usepackage{float}
%% \let\labelindent\relax
%% \usepackage{enumitem}
%% \usepackage{hyperref}
%% \usepackage{tabu}
%% \usepackage{array}
%% \usepackage{caption}
%% \usepackage{subcaption}
%% \usepackage{colortbl}
%% \usepackage{tikz}
%% \usepackage{algorithm}
%% \usepackage{algpseudocode}
%% \usepackage{xparse}
%% \usetikzlibrary{positioning}
%% \usetikzlibrary{bayesnet}

%% \usepackage{biblatex}
%% \addbibresource{bibliography.bib}

%% \DeclareLabelname[movie]{
%%   \field{director}
%%   \field{producer}
%% }
\newcommand{\programSpace}{\vspace{0.2in}}
\newcommand{\programTime}[1]{\textbf{$\sim\sim$ #1 $\sim\sim$}}

\title{\LARGE \bf
  Marriage between \\
  Bradley Larkin Saund and Kathryn Mary Brennan
}


\author{Brad Saund and Katie Brennan$^{\dagger}$
\thanks{${^\dagger}$Equal contribution from both authors}%
}


\begin{document}



\maketitle
\thispagestyle{empty}
\pagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  We propose a novel union between Bradley Larkin Saund and Kathrn Mary Brennan\footnote{Soon to be Kathryn Mary Saund}.
  Prior marriages, such as those of our parents, provide a strong background and inspiration for us going forward.
  Our relationship over the past six years indicates many years of love to follow.
  We look to our beloved friends and family here today for support thoughout the rest of our lives.
  We predict this marriage will last till death do us part.
  
\end{abstract}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Marriage is what brings us together today\cite{PrincessBride}.
And so, we are finally getting married\cite{AladdinKoT}.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background}
Charles Darwin has pondered the rational for marriage between humans, and we repeat his musings below:\\
``\textbf{Reasons to marry:} Children (if it Please God), Constant companion (\&friend in old age) who will feel interested in one, object to be beloved \& played with - better than a dog anyhow, home \& someone to take care of house, Charms of music \& female chit-chat. These things good for one's health, but terrible loss of time.\\
\textbf{Reasons not to marry:} Freedom to go where one liked - choice of Society \& little of it. Conversation of clever men at clubs - Not forced to visit relatives, \& to bend in every trifle. - to have the expense \& anxiety of children - perhaps quarelling, Loss of time - cannot read in the Evenings, fatness \& idleness, less money for books, if many children forced to gain one's bread.

If one does not marry soon, one misses so much good pure happiness.''\cite{Darwin}


\vspace{1.5in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Program}
\programSpace
\begin{center}
  \programTime{5:00}\\
  Marriage Ceremony\\
  \programSpace

  \programTime{6:30}\\
  Dinner\\
  \programSpace

  \programTime{8:00}\\
  Reception

  \programSpace
  
\end{center}
\section{Conclusion}
Brad and Katie are getting married on May 13, 2017.

\section{Acknowledgements}
We would like to thank our Bridal Party of Rachel Brennan, Cameron and Meridith Brennan, and Carolyn Saund.
We also thank Carson McNeil serving as our officiant.

\bibliographystyle{IEEEtran}
%% \bibliographystyle{plain}
\bibliography{bibliography}
%% \printbibliography

\end{document}
